---
title: "Descriptive Analysis"
output: html_document
---

## The dataset
The statistical units are the bombs exploded in the first 24 hours of the bombing of London, on September 7th, 1940. For each bomb the following informations are provided:
- Order
- Time (IB: Incendiary Bomb, EB: Explosive Bomb, COB: Crude Oil Bomb)
- Location
- Type of bomb
- Damage or other details ("Damage.or.other.details..All.dimensions.at.in.ft.unless.stated.")           )

We got data about 843 bombs.

Loading:
```{r}
data_path <- "../data/September 7, 1940_ first night of the Blitz - SEPT 7, ALL REPORTS.csv"
bomb_data <- read.csv(file = data_path)
bomb_data$X <- NULL

colnames(bomb_data) <- c("Order", "Time", "Location", "Type.of.bomb", "Damage.or.other")
```

## Preprocessing:
- coverting strings into POSIX type
```{r}
bomb_data$Time <- strptime(bomb_data$Time, format = "%H:%M")
```
- getting Latitude and Longitude from the addresses [(geocoding)](https://www.r-bloggers.com/2023/03/how-to-geocode-in-r-for-free/)
```{r eval=FALSE, include=FALSE}
library(tidyverse)
library(sf)
library(mapview)

geocodes <- tidygeocoder::geocode(
              .tbl = bomb_data,
              address = Location,
              method = "osm"
            )
  
```
- cleaning duplicates in type of bomb
```{r}
bomb_data$Type.of.bomb <- as.factor(bomb_data$Type.of.bomb)

levels(bomb_data$Type.of.bomb) <- list(IB = c("IB", "Ib", "IBIB"),
                                       EB = c("EB", "EB ", "eb", "Eb", "High Explosive Bomb"),
                                       EB.and.IB = c("EB & IB", "EB &IB", "EB &IB", "IB & EB", "IB and EB"),
                                       Magnesium.Flare = c("Magnesium Flare"),
                                       Shrapnel = c("Shrapnel"),
                                       COB = c("COB", "Crude oil bomb"),
                                       Crashed.Aircraft = c("Crashed aircraft"),
                                       Unknow.enemy.action = c("Unknown enemy action"))

```

```{r eval=FALSE, include=FALSE}
write.csv(bomb_data, file = "../data/preprocessed_bombing.csv")
```


## Descriptive analysis
```{r}
#Time
hist(bomb_data$Time, breaks = "hours", las=2)

#Type of bomb
barplot(table(bomb_data$Type.of.bomb), las=2)

#Type of bomb by time
hist(bomb_data[bomb_data$Type.of.bomb == "IB",]$Time, breaks = "hours", las=2)
hist(bomb_data[bomb_data$Type.of.bomb == "EB",]$Time, breaks = "hours", las=2)
hist(bomb_data[bomb_data$Type.of.bomb == "EB.and.IB",]$Time, breaks = "hours", las=2)
hist(bomb_data[bomb_data$Type.of.bomb == "COB",]$Time, breaks = "hours", las=2)

```
